NumPy---Array Computation for Python

### 2020-01-03 authors.tex
Rework history, funding, and current status sections (w/ Jarrod Millman)
Restructure second section

\author[1]{Charles R Harris}
\author[2]{Travis E. Oliphant}
\author[3,*]{St\'efan J. van der Walt}
\author[3]{Warren Weckesser}
\author[3,4,*]{K. Jarrod Millman}
\author[5]{Kevin Sheppard}
\affil[1]{Independent Researcher}
\affil[2]{Quansight LLC, Austin, TX, USA}
\affil[3]{Berkeley Institute for Data Science, University of California, Berkeley, CA 94720, USA}
\affil[4]{Division of Biostatistics, University of California, Berkeley, CA 94720, USA}
\affil[*]{numpy.articles@gmail.com}
\affil[5]{kevin.sheppard@economics.ox.ac.uk, Department of Economics, University of Oxford, Oxford, OX1 3UQ, UK}

>>>>

\author[1]{Charles R Harris}
\author[2,*]{St\'efan J. van der Walt}
\author[3,*]{Ralf Gommers}
\author[2,4,*]{K. Jarrod Millman}
\author[2]{Sebastian Berg}
\author[5]{Kevin Sheppard}
\author[6]{Tyler J. Reddy}
\author[2]{Warren Weckesser}
\author[3]{Travis E. Oliphant}
\affil[1]{Independent Researcher}
\affil[2]{Berkeley Institute for Data Science, University of California, Berkeley, CA 94720, USA}
\affil[3]{Quansight LLC, Austin, TX, USA}
\affil[4]{Division of Biostatistics, University of California, Berkeley, CA 94720, USA}
\affil[5]{Department of Economics, University of Oxford, Oxford, OX1 3UQ, UK}
\affil[6]{Los Alamos National Laboratory, Los Alamos, NM 87544, USA}
\affil[*]{numpy.articles@gmail.com}

### 2020-01-03 body.tex
Restructure second section

\section{Organization and infrastructure}

@@

The NumPy library consists of core functionality (e.g., the NumPy array data structure),
functions for manipulating arrays and doing scientific computation, and infrastructure
libraries.

\subsection{Core functionality}

The \code{ndarray} data structure stores regularly spaced elements of a single
data type in a contiguous block of memory; along with meta-data such as shape,
it allows for the efficient representation of $n$-dimensional arrays.
More details about the data structure are given in ``The NumPy array:
a structure for efficient numerical computation.''\cite{vanderwalt2011numpy}.

@@

\subsection{Computing libraries}

\subsection{Infrastructure libraries}

>>>>

\section{Community and library}

@@

\subsection{Basic functionality}

The \code{ndarray} data structure stores regularly spaced elements of a single
data type in a contiguous block of memory; along with meta-data such as shape,
it allows for the efficient representation of $n$-dimensional arrays.
\fixme{discuss Figure~\ref{fig:basic-functionality} .. vectors / matrices / and then more ...}
More details about the data structure are given in ``The NumPy array:
a structure for efficient numerical computation.''\cite{vanderwalt2011numpy}.

\begin{figure}
\centering
\begin{subfigure}{.5\textwidth}
\begin{lstlisting}
>>> import numpy as np
>>> x = np.array([0, 1, 2, 3])
>>> x.dtype
dtype('int64')
>>> x.shape
(4,)

>>> y = 2 * x
>>> y
array([0, 2, 4, 6])

>>> x * y
array([ 0,  2,  8, 18])

>>> x @ y
28
\end{lstlisting}
  \caption{Vectors (1-d arrays)}
  \label{fig:sub1}
\end{subfigure}%
\begin{subfigure}{.5\textwidth}
\begin{lstlisting}
>>> import numpy as np
>>> x = np.array([1, 2])
>>> A = np.array([[0.1, 0.2], [0.3, 0.2]])
>>> A.dtype 
dtype('float64')
>>> A.shape
(2, 2)

>>> A * x
array([[0.1, 0.4],
       [0.3, 0.4]])

>>> A @ x
array([0.5, 0.7])
>>> x @ A
array([0.7, 0.6])
\end{lstlisting}
  \caption{Vectors (1-d arrays) and Matrices (2-d arrays)}
  \label{fig:sub2}
\end{subfigure}
\caption{Basic functionality}
\label{fig:basic-functionality}
\end{figure}

\subsection{Advanced functionality}

@@
